##Loading and preprocessing the data

```{r}
df <- read.csv("activity.csv")
gd <- complete.cases(df)
dfg <- df[gd,]
ag <- aggregate(steps ~ interval, data=dfg, mean)

```
##What is mean total number of steps taken per day

```{r}
hist(ag$steps, main="Histogram of Number of Steps", xlab="Number of steps")
summary(ag)
```
**From the above data it is evident that the mean of number of steps is 37.38 and the meadian is 34.113**

##What is the average daily activity pattern?

```{r}
plot(ag[,1],ag[,2], type="l", xlab="Interval", ylab="Number of Steps", main="Plot of Interval and number of steps")
```

**asserted by the graph maximum value is 206 and it is for and was between interval of 830 to 835**

##Imputing missing values
```{r}
dfng <- df[!gd,]
dim(dfng)
mg <- merge(dfng,ag,by.x="interval",by.y="interval") ##Merging the average values with dataframe of NAs
mgg <- merge(df,mg,by.x="date",by.y="date") ##Merging the values of NA with that of the original data frame
colnames(mgg)[6] <- "Nsteps"
agg <- aggregate(Nsteps~interval.y, data=mgg, mean)
hist(agg[,2], main="Histogram of Number of Steps", xlab="Number of steps")
summary(agg)

```

**From the above data it is evident that the number of NAs are 2304**
**Mean of the values is 37.383 and the median is 34.113**
**Did not find much difference after imputing NAs**



##